Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-24 Paper/Paper.tex
intro thing about beat alignment added

One major issue in working with small patches concerns temporal
alignment.  FIXME: [explain bar alignment]

@@

%\subsection{Harmonic Patterns}
\subsection{Beat-Chroma Patches}
% Patterns are defined as a number of beats or bars. In the case of beats,
% we simply cut the set of chromas per beat every $N$ beats. In the case
% of bars, we gather all beats corresponding to the $N$ bars requested.
% The number of chroma vectors we get can vary. We resize the features in the
% time axis to a fixed length. Resizing over clipping can be argued over, 
% but it should
% preserve the main bar characteristics (such as a strong beat at the beginning
% or a note change in the middle).

@@

Another interesting visualization uses LLE\footnote{implementation:
  \url{http://www.astro.washington.edu/users/vanderplas/coding/LLE/}}
algorithm \cite{Roweis2000} to display codewords arranged in
coherent groups. See Figure \ref{fig:lle}.

>>>>

One major issue in working with small patches concerns temporal
alignment. Learning the same motifs with different offset
(of a few seconds, or audio frames) is redundant. We take advantage
of rythmic knowledge about the song to align patches with beats.
We can further group beats into bars, meaningful music segments.
The use of the Echo Nest API \cite{EchoNest} for that purpose is 
explained in Subsection \ref{ssec:beatpatch}. Patches built around
those temporal landmarks should capture music motifs more easily.

@@

%\subsection{Harmonic Patterns}
\subsection{Beat-Chroma Patches} \label{ssec:beatpatch}
% Patterns are defined as a number of beats or bars. In the case of beats,
% we simply cut the set of chromas per beat every $N$ beats. In the case
% of bars, we gather all beats corresponding to the $N$ bars requested.
% The number of chroma vectors we get can vary. We resize the features in the
% time axis to a fixed length. Resizing over clipping can be argued over, 
% but it should
% preserve the main bar characteristics (such as a strong beat at the beginning
% or a note change in the middle).

@@

Another interesting visualization uses LLE\footnote{implementation:
  \url{http://www.astro.washington.edu/users/vanderplas/coding/LLE/}}
algorithm \cite{Roweis2000} to display codewords arranged in
coherent groups. See Figure \ref{fig:lle}. FOr instance, we see
``wideband'' patterns grouping to the right.
